The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-09 paper.tex
update

  First, the broad agreement between simulated and observed X-ray map hint that\
  the symmetric eROSITA bubbles can be properly formed by an inclined jet within a thin disk\
  of dense interstellar medium.\

>>>>

  First, the broad agreement between simulated and observed X-ray map hint that\
  the full vertical extent of the eROSITA bubbles can be properly formed by an inclined jet within a thin disk\
  of dense interstellar medium.\
